Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-16 paper.tex
Forgot to push :/

\todo{Add section numbers to the figure}\note{TR: put this into a proper figure, add known danvy sequence 
for concrete evaluators at the bottom (in grey or dashed lines)}

@@

It is worth noting that the continuation class @Kont@ is defined as a list of
frames.
The frame can be considered as evaluation context in reduction semantics.
The frame class @Frame@ stores the information of a single call-site,
i.e., the information that can be used to resume the interrupted computation.
A @Frame@ constitutes of a variable name @x@ to be bind later, a control expression
that resumes to, and its environment. (TODO: mention that frame list vs KArg/KFun)

\subsubsection{Single-step Transition}
Before going into describing how the machine evaluates expressions, we firstly define several helper functions.
As we mentioned in section \ref{anfsyntax}, the atomic expressions are either a variable, or
a literal @lambda@ term. So the atomic expression evaluator @atomicEval@ handles these two
cases and evaluates atomic expressions to closures in a straightforward way.
The @alloc@ function generates a fresh address, and always allocates unique integer
in the domain of store.
The @isAtomic@ function is used as a predicate of the expression is atomic.

@@

Now, we can faithfully describe the state transition function @step@,
that given a machine state, determines its successor state.

>>>>

\todo{Add section numbers to the figure}\note{TR: put this into a proper figure, add known danvy sequence
for concrete evaluators at the bottom (in grey or dashed lines)}
\note{JD: should these be abstracting abstract machines?}

@@

It is worth noting that the continuation class @Kont@ is defined as a list of
frames, where a frame can be considered an evaluation context in reduction semantics.
We represent frames using the @Frame@ class, which stores the information of a single
call-site, i.e., the information that can be used to resume the interrupted computation.
A @Frame@ constitutes a variable name @x@ to be bound later, a control expression
to which the program may resume, and its environment. \note{JD: someone check this and make sure I got it right}
\todo{mention that frame list vs KArg/KFun}

\subsubsection{Single-Step Transition}
Before describing how the machine evaluates expressions, we must first define several helper
functions. As mentioned in Section~\ref{anfsyntax}, atomic expressions are either a variable
or a literal @lambda@ term. As such, the atomic expression evaluator @atomicEval@ handles
these two cases and evaluates atomic expressions to closures in a straightforward way.
The @alloc@ function generates a fresh address, and always allocates unique integer
in the domain of store.
The @isAtomic@ function is used as a predicate to determine if the expression is atomic.

@@

Now, we can faithfully describe the state transition function @step@,
that, when given a machine state, determines its successor state.
